Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-09-01 doc/main_jfm.tex
done up to end of 4.4

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Vesicle in a Parabolic Flow}
Another interesting flow to consider is the parabolic flow
\begin{align}
  \uu_\infty = v_{max}\left[ 1 - \left( \frac{y}{wR_0}\right)^2
    \right]\mathbf{e}_x,
\end{align}
%
where $v_{max}$ is the flow strength and $w$ determines the shape of the
flow. $R_0$ is defined as the radius of the JP vesicle at $t=0$. The
behavior of a vesicle in this unbounded non-linear flow includes
vertical migration, and depending on the flow rate and reduced area, the
steady-state shape can be either an symmetric parachute or an asymmetric
slipper~\cite{Kaoui09, cou-kao-pod-mis2008, dan-vla-mis2009}.

@@

Figure~\ref{figure6} shows three configurations for one specific case
where the centroid of the JP vesicle is initially placed slightly
above the $x$-axis. The parameters are $v_{max} = 8.0$, $w=10$, and
$R_0=8$. The red curves are the midplanes and a particle pair is marked
in color. We observe that the deformed JP vesicle has a
counterclockwise movement and the shape of the vesicle approaches an
asymmetric slipper shape. For this test, the reduced area for this
configuration is approximately $0.9$ which matches the previous
numerical tests in~\cite{Kaoui09} where a slipper-like shape occurs when
the flow velocity is weak and the reduced area is large. A schematic of
the setup is shown in Figure~\ref{figure7} where the blue horizontal
line represents the mean $y$-position of all particles. The inset of
Figure~\ref{figure7} shows the trajectory of the mean position in the
$y$-direction which decreases toward $y=1$ for a period of time and then
starts to have an oscillatory motion due to the granularity of the
JP vesicle.

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{slipper.eps}
  \caption{\label{figure6} A JP vesicle suspended in a parabolic flow
  where the strength of the flow is $v_{max}=32.8$~nm ns$^{-1}$, $R_0 =
  20$~nm, and the control parameter is $w=25$~nm. The configuration is
  the state when $t=\{0, 4000, 8000\}$. The red curves are the
  midplanes.}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=2in]{parabolic.eps}
  \caption{\label{figure7} The schematic of a JP vesicle suspended in
  a parabolic flow where the strength of the flow is $v_{max}=32.8$~nm
  ns$^{-1}$, $R_0 = 20$~nm, and the control parameter is $w=25$~nm. The
  configuration is generated when $t=10000$. The inset plots the
  trajectory of mean $y$-position over the time.}
\end{figure}

@@

With the choice of a large shear rate, a pore formation or a complete
membrane rupture can occur. Figure~\ref{figure8} demonstrates how a
vesicle under a shear flow with shear rate $\chi=0.1$ can rupture. The
streamlines are included in these plots. An interesting phenomenon
occurs in panels (c) and (d) where two separated bilayers move along the
background shear flow symmetrically.  Consequently, a periodic motion
for bilayers may occur with the choices of shear rates. One can expect
that these two layers will flow far apart from each other for much
higher shear rates.

\begin{figure}
\centering
\includegraphics[height=2in]{N58_rupt_0.pdf}
\includegraphics[height=2in]{N58_rupt_200.pdf}
\\
\includegraphics[height=2in]{N58_rupt_400.pdf}
\includegraphics[height=2in]{N58_rupt_600.pdf}
  \caption{\label{figure8} Membrane rupture occurs when the shear rate
  exceeds a threshold. Here the shear rate is $\chi = 0.1$.  Starting
  with a circular shape (panel (a)), the vesicle is stretched by the
  background flow and multiple pores appear (panel (b)).  Panels
  (c)--(d) show the later states during the simulation. Streamlines are
  included in each panel.}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Vesicle in a Parabolic Flow}
Another interesting flow to consider is the parabolic flow
\begin{align}
  \uu_\infty = v_{max}\left[ 1 - \left( 
    \frac{\xx \cdot \mathbf{e}_y}{wR_0}\right)^2
    \right]\mathbf{e}_x,
\end{align}
%
where $v_{max}$ is the flow strength and $w$ determines the shape of the
flow. $R_0$ is defined as the radius of the JP vesicle at $t=0$. The
behavior of a vesicle in this unbounded non-linear flow includes
vertical migration, and depending on the flow rate and reduced area, the
steady-state shape can be either a symmetric parachute or an asymmetric
slipper (\cite{Kaoui09, cou-kao-pod-mis2008, dan-vla-mis2009}).

@@

Figure~\ref{figure6} shows three configurations for one specific case
where the centroid of the JP vesicle is initially placed slightly
above the $x$-axis. The parameters are $v_{max} = 8.0$, $w=10$, and
$R_0=8$. The red curves are the midplanes and a particle pair is marked
in color. We observe that the deformed JP vesicle has a
counterclockwise movement and the shape of the vesicle approaches an
asymmetric slipper shape. Moreover, we observe inter-monolayer slip
between the two leaflets. For this test, the reduced area for this
configuration is approximately $0.9$ which matches the previous
numerical tests in~\cite{Kaoui09} where a slipper-like shape occurs when
the flow velocity is weak and the reduced area is large. A schematic of
the setup is shown in Figure~\ref{figure7} where the blue horizontal
line represents the mean $y$-position of all particles. The inset of
Figure~\ref{figure7} shows the trajectory of the mean position in the
$y$-direction that decreases towards $y=1$ for a period of time and then
starts to oscillate due to the granularity of the JP vesicle.

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{slipper.eps}
  \caption{\label{figure6} A JP vesicle suspended in a parabolic flow
  where the strength of the flow is $v_{max}=32.8$~nm ns$^{-1}$, $R_0 =
  20$~nm, and the control parameter is $w=25$~nm. The configuration is
  the state when $t=\{0, 4000, 8000\}$. The red curves are the
  midplanes. Inter-monolayer slip is observed by comparing the relative
  locations of the blue and yellow particles.}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=2in]{parabolic.eps}
  \caption{\label{figure7} The schematic of a JP vesicle suspended in a
  parabolic flow where the strength of the flow is
  $v_{max}=32.8$~nm~ns$^{-1}$, $R_0 = 20$~nm, and the control parameter
  is $w=25$~nm. The configuration occurs when $t=10000$. The inset plots
  the trajectory of mean $y$-position over time.}
\end{figure}

@@

A pore formation or a complete membrane rupture can occur at large shear
rates. Figure~\ref{figure8} demonstrates how a vesicle can rupture when
suspended in a shear flow with shear rate $\chi=0.1$. The streamlines
are included in these plots. An interesting phenomenon occurs in panels
(c) and (d) where two separated bilayers move along the background shear
flow symmetrically. Consequently, a periodic motion for bilayers may
occur at certain shear rates. One can expect that these two layers will
diverge from one another for much higher shear rates.

\begin{figure}
\centering
\includegraphics[height=2in]{N58_rupt_0.pdf}
\includegraphics[height=2in]{N58_rupt_200.pdf}
\\
\includegraphics[height=2in]{N58_rupt_400.pdf}
\includegraphics[height=2in]{N58_rupt_600.pdf}
  \caption{\label{figure8} Membrane rupture occurs when the shear rate
  exceeds a threshold. Here the shear rate is $\chi = 0.1$. Starting
  with a circular shape (panel (a)), the vesicle is stretched by the
  background flow and multiple pores form (panel (b)). Panels (c)--(d)
  show the later states during the simulation. Streamlines are included
  in each panel.}
\end{figure}
